Comparing Parallel Sorting Algorithms on a High Performance Computing Cluster Using OpenMP

### 2020-11-16 paper/Paper.tex
fixed figs, added emails

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
		T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
		\title{Comparing Parallel Sorting Algorithms on a High Performance Computing Cluster Using OpenMP}
			\author{\IEEEauthorblockN{Benjamin Pierce}
			\IEEEauthorblockA{
				\textit{Department of Computer and Data Sciences}\\ }
			\and
			\IEEEauthorblockN{Alberto Safra}
			\IEEEauthorblockA{ 
				\textit{Department of Computer and Data Sciences}}
			\and
			\IEEEauthorblockN{Colin Causey}
			\IEEEauthorblockA{ 
			\textit{Department of Computer and Data Sciences}}
			\and
			\IEEEauthorblockN{Jason Richards}
			\IEEEauthorblockA{
				\textit{Department of Computer and Data Sciences}}}
	\maketitle

@@

\subsection{Quicksort}
There was great success with parallel Quicksort. 
As a divide-and-conquer algorithm, it is a naturally parallel algorithum. 
The results of this algorithum can be seen in Figure \ref{qck_per}. 
\begin{figure}[h]
	\includegraphics[width=10.5cm]{qs_mt.png} 
	\caption{Performance of Quicksort}
	\label{qck_per}
\end{figure}

@@

\subsection{Comparative Results}
Results are compared in a few different ways. 
One is to hold the number of threads constant, and plot the performance of each algorithm, as in Figure \ref{msqshs}, which shows that Heapsort, which is not paralleized, proves to be much worse then either Quicksort or Mergesort.
\begin{figure}
	\includegraphics[width=10.5cm]{mshsqs.png} 
	\caption{Comparative Performance with 8 threads}
	\label{msqshs}
\end{figure}
%TODO Add deets
Additionally, it is useful to compare results on a single array size with multiple threads. 
This can be seen for $10^6$ elements in Figure \ref{1e5}
\begin{figure}[h]
	\includegraphics[width=9cm]{1e5.png} 
	\caption{Comparative Performance with for $10^4$ elements}
	\label{1e5}
\end{figure}
Interestingly, the performance of Quicksort appears to worsen with the number of threads more then Mergesort; this suggests significant overhead introduced by parallelization. 
However, this effect goes away with an increase in the number of elements, as in Figure \ref{1e8}. 
\begin{figure}[h]
	\includegraphics[width=9cm]{1e8.png} 
	\caption{Comparative Performance with for $10^7$ elements}
	\label{1e8}
\end{figure}

>>>>

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
        T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
    \title{Comparing Parallel Sorting Algorithms on a High Performance Computing Cluster Using OpenMP}
    \author{\IEEEauthorblockN{Benjamin Pierce\\\href{mailto:bgp12@case.edu}{bgp12@case.edu}}
        \IEEEauthorblockA{
            \textit{Department of Computer and Data Sciences}\\ }
        \and
        \IEEEauthorblockN{Alberto Safra\\\href{mailto:axs1249@case.edu}{axs1249@case.edu}}
        \IEEEauthorblockA{ 
            \textit{Department of Computer and Data Sciences}}
        \and
        \IEEEauthorblockN{Colin Causey\\\href{mailto:cjc158@case.edu}{cjc158@case.edu}}
        \IEEEauthorblockA{ 
            \textit{Department of Computer and Data Sciences}}
        \and
        \IEEEauthorblockN{Jason Richards\\\href{mailto:jdr145@case.edu}{jdr145@case.edu}}
        \IEEEauthorblockA{
            \textit{Department of Computer and Data Sciences}}}
    \maketitle

@@

    \subsection{Quicksort}
    There was great success with parallel Quicksort. 
    As a divide-and-conquer algorithm, it is a naturally parallel algorithum. 
    The results of this algorithum can be seen in Figure \ref{qck_per}. 
    \begin{figure}[h]
        \includegraphics[width=9.25cm]{qs_mt.png} 
        \caption{Performance of Quicksort}
        \label{qck_per}
    \end{figure}

@@

    \subsection{Comparative Results}
    Results are compared in a few different ways. 
    One is to hold the number of threads constant, and plot the performance of each algorithm, as in Figure \ref{msqshs}, which shows that Heapsort, which is not paralleized, proves to be much worse then either Quicksort or Mergesort.
    \begin{figure}
        \includegraphics[width=9.25cm]{mshsqs.png} 
        \caption{Comparative Performance with 8 threads}
        \label{msqshs}
    \end{figure}
    %TODO Add deets
    Additionally, it is useful to compare results on a single array size with multiple threads. 
    This can be seen for $10^6$ elements in Figure \ref{1e5}
    \begin{figure}
        \includegraphics[width=9cm]{1e5.png} 
        \caption{Comparative Performance with for $10^4$ elements}
        \label{1e5}
    \end{figure}
    Interestingly, the performance of Quicksort appears to worsen with the number of threads more then Mergesort; this suggests significant overhead introduced by parallelization. 
    However, this effect goes away with an increase in the number of elements, as in Figure \ref{1e8}. 
    \begin{figure}
        \includegraphics[width=9cm]{1e8.png} 
        \caption{Comparative Performance with for $10^7$ elements}
        \label{1e8}
    \end{figure}
